Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-26 main_paper.tex
Minor changes to text on Section 3 and beggining of Section 4.

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_{n}$ and $b_{n}$ are bandwidths as described by Assumption~\ref{A2} and define
  \begin{align}
    I^{-}(h) &= \{i : h < X_{i} < 0\}, &
    I^{+}(h) &= \{i : 0 < X_{i} < h\}.
  \end{align}
  Also define $M^{-}(h_{n})$ and $M^{+}(h_{n})$ to be the number of elements in
  $I^{-}(h_{n})$ and $I^{+}(h_{n})$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_{p+1}^+(X_{i}) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:2}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
incorporate that dependency into our notation by wrting
$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_1$ is large enough that it can be ignored and
define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component and
this estimator converges to zero fast enough in probability that it can be be
used as a correction. As is standard in the bootstrap literature, we will assume
that the number of bootstrap replications, $B_1$, is large enough that the
simulation error can be ignored.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
  $(\hat\tau(h_n,b_n) - \Delta^*(h_n,b_n) - \tau) / V^{1/2}(h_n, b_n) \to^d N(0,1)$.
\end{theorem}

With Algorithm~\ref{Alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$. Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm~\ref{Alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap. Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$. These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h_{n},b_{n})$ in the asymptotic variance formula on Section \ref{background}.

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_i =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

@@

We selected three data generating processes (DGP) that are widely used in the RD literature to evaluate the performance of the proposed bootstrap procedure, those are the same chosen by CCT and \cite{IK} and provide a good testing ground for bias correction due to their exacerbated curvature. To be specific, the pseudo data are generated as 500 i.i.d. draws from:
\begin{align*}
& Y_{i} = \mu_{j}(X_{i}) + \epsilon_{i}, \;\;\; X_{i} \sim  (2 B (2,4) - 1)), \\
& \epsilon_{i} \sim N(0, \sigma^{2}), \;\;\; \sigma = 0.1295, \;\;\; j = 1,2,3.
\end{align*}
Three different choices of functional forms for $\mu_{j}(x)$ are as follows:
\begin{align}
\mu_{1}(x) & = 
\begin{cases}
0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}, \;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5},  & \text{if} \;\; x \ge 0.
\end{cases}
\\
\mu_{2}(x) & = 
\begin{cases}
3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5, \;\; & \text{if} \;\; x < 0, \\
0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5,  & \text{if} \;\; x \ge 0.
\end{cases}
\\
\mu_{3}(x) & =
\begin{cases}
0.48 + 1.27x + 0.5 \times 7.18x^{2}+ \\
+ 0.7 \times 20.21x^3 + 1.1 \times 21.54x^4 + 1.5 \times 7.33x^5, \;\;\;\;\;\;\;\;\;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 0.1 \times 3.00x^{2}+ \\
+ 0.3 \times 7.99x^3 - 0.1 \times 9.01x^4 + 3.56x^5, & \text{if} \;\; x \ge 0.
\end{cases}
\end{align}

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by \cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach. For each DGP, we used four methods to obtain point estimate and 0.95 confidence interval. For each method, a total 1500 replications were performed. The first two methods follow CCT procedure with triangular and uniform kernel. The third and fourth methods follow the bootstrap procedure with uniform kernel. The only difference between the last two is that one is bias corrected and the other is not. In the bootstrap procedure, we used 500 bootstraps for bias correction, 999 bootstraps to calculate confidence interval. Table \ref{Tb: simulation 1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$). Table \ref{Tb: simulation 2} presents similar results for $p=2$ and $q=3$.

\begin{table}[t]
\centering
\begin{tabular}{rrrrrrrrr}
  \toprule
	DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
	1 & $CCT_{tri}$ & -0.010 & 0.068 & 0.068 & 0.911 & 0.241 \\ 
	  & $CCT_{uni}$ & -0.016 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
	  & $bootstrap_{uni}$       & -0.018 & 0.066 & 0.069 & 0.931 & 0.240 \\ 
	  & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.060 & 0.064 & 0.916 & 0.208 \\
	\midrule
	2 & $CCT_{tri}$ & -0.011 & 0.085 & 0.086 & 0.935 & 0.343 \\ 
	  & $CCT_{uni}$ & -0.010 & 0.087 & 0.088 & 0.938 & 0.350 \\ 
	  & $bootstrap_{uni}$       & -0.012 & 0.088 & 0.089 & 0.953 & 0.324 \\ 
	  & $bootstrap_{uni}^{nbc}$ & -0.051 & 0.086 & 0.100 & 0.869 & 0.300 \\ 
	\midrule
	3 & $CCT_{tri}$ & -0.008 & 0.067 & 0.067 & 0.919 & 0.246 \\ 
	  & $CCT_{uni}$ & -0.004 & 0.065 & 0.065 & 0.943 & 0.250 \\ 
	  & $bootstrap_{uni}$       & -0.004 & 0.064 & 0.064 & 0.960 & 0.246 \\ 
	  & $bootstrap_{uni}^{nbc}$ & 0.016 & 0.062 & 0.064 & 0.931 & 0.218 \\ 
  \bottomrule
\end{tabular}
\caption{Summary of estimates ($p = 1, q = 2$)}
\label{Tb: simulation 1}
\end{table}

As can be seen on the tables, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain 
valid robust confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT. The results also demonstrate the importance of bias correction when huge kink 
presents at the cutoff (such as in the second DGP). Failing to correct bias in this case leads to a confidence interval with incorrect coverage.

\begin{table}[t]
\centering
\begin{tabular}{rrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
    1 & $CCT_{tri}$ & -0.006 & 0.079 & 0.079 & 0.923 & 0.291 \\ 
      & $CCT_{uni}$ & -0.003 & 0.081 & 0.081 & 0.932 & 0.299 \\ 
      & $bootstrap_{uni}$       & -0.003 & 0.079 & 0.079 & 0.947 & 0.294 \\ 
      & $bootstrap_{uni}^{nbc}$ & -0.008 & 0.073 & 0.074 & 0.941 & 0.261 \\ 
     \midrule
    2 & $CCT_{tri}$ & -0.007 & 0.080 & 0.080 & 0.941 & 0.319 \\ 
      & $CCT_{uni}$ & -0.005 & 0.081 & 0.081 & 0.946 & 0.326 \\ 
      & $bootstrap_{uni}$       & -0.008 & 0.080 & 0.080 & 0.955 & 0.300 \\ 
      & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.075 & 0.078 & 0.924 & 0.273 \\ 
     \midrule
    3 & $CCT_{tri}$ & 0.004 & 0.080 & 0.080 & 0.922 & 0.291 \\ 
      & $CCT_{uni}$ & -0.004 & 0.082 & 0.082 & 0.931 & 0.296 \\ 
      & $bootstrap_{uni}$       & 0.002 & 0.077 & 0.077 & 0.958 & 0.294 \\ 
      & $bootstrap_{uni}^{nbc}$ & -0.001 & 0.073 & 0.073 & 0.948 & 0.260 \\ 
  \bottomrule
\end{tabular}
\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
\label{Tb: simulation 2}
\end{table}

>>>>

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h_{n}$ and $b_{n}$ are bandwidths as described by Assumption~\ref{A2} and define
  \begin{align}
    I^{-}(h) &= \{i : h < X_{i} < 0\}, &
    I^{+}(h) &= \{i : 0 < X_{i} < h\}.
  \end{align}
  Also define $M^{-}(h_{n})$ and $M^{+}(h_{n})$ to be the number of elements in
  $I^{-}(h_{n})$ and $I^{+}(h_{n})$ respectively.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:1}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_{p+1}^+(X_{i}) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation}
      \label{eq:2}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation}
  \end{enumerate}
\end{algorithm}
The distribution of $\Delta^{*}$ depends on $B_{1}$ and we could
incorporate that dependency into our notation by writing $\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_{1}$ is large enough that it can be ignored and define $\Delta^* = \plim_{B_{1} \to \infty} \Delta^*_{B_{1}}$

Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
converges fast enough in probability that it can be be used as a correction. As is standard in the bootstrap literature, we will assume
that the number of bootstrap replications, $B_{1}$, is large enough that the simulation error can be ignored.

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{align}
  \frac{(\hat\tau(h_{n},b_{n}) - \Delta^{*}(h_{n},b_{n}) - \tau)}{ V^{1/2}(h_n, b_n)} \to^{d} N(0,1)
\end{align}
\end{theorem}

With Algorithm~\ref{Alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$. Here the idea is similar, but now we actually calculate a bias corrected estimate using Algorithm~\ref{Alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap. Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$. These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h_{n},b_{n})$ in the asymptotic variance formula on Section \ref{background}.

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I^{-}$, $I^{+}$, $M^{-}$, and $M^{+}$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
    Equation --- and define the residuals
    \begin{equation}
      \label{eq:3}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_i - \hat g_{p+1}^+(X_{i}) & \otherwise
      \end{cases}
    \end{equation}
  \item Repeat the following steps $B_{2}$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_{2}}^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^{-}(b_{n})$ from
      $\{\hat\varepsilon_{i} : i \in I^{-}(b_{n})\}$ and one of size $M^{+}(b_{n})$ from
      $\{\hat\varepsilon_i : i \in I^{+}(h_{n})\}$. Let $\varepsilon_{i}^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
      \end{equation*}
      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

@@

We adopt the same three data generating processes (DGP) used by CCT to make it easy to compare our results. Also, these DGPs are widely used in the RD literature to evaluate the performance of inference procedures and provide a good testing ground for bias correction due to their exacerbated curvature.

For all Monte Carlo experiments, the pseudo data are generated as 500 i.i.d. draws from:
\begin{align*}
& Y_{i} = \mu_{j}(X_{i}) + \epsilon_{i}, \;\;\; X_{i} \sim  (2 B (2,4) - 1)), \\
& \epsilon_{i} \sim N(0, \sigma^{2}), \;\;\; \sigma = 0.1295, \;\;\; j = 1,2,3.
\end{align*}
Regarding the functional form for $\mu(x)$ in each DGP, the first one is based on a fifth order polynomial fitted on the data observed by \cite{lee2008rand} when estimating the incumbency advantage in electoral races to the U.S. House of Representatives. Hence, $\mu_{1}(x)$ is given by,
\begin{align}
\mu_{1}(x) & = 
\begin{cases}
0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}, \;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5},  & \text{if} \;\; x \ge 0.
\end{cases}
\end{align}

The functional form for $\mu_{2}(x)$, in the second DGP follows the data observed by \cite{ludwig2007}, which we examine in more detail on Section \ref{application}, and follows
\begin{align}
\mu_{2}(x) & = 
\begin{cases}
3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5, \;\; & \text{if} \;\; x < 0, \\
0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5,  & \text{if} \;\; x \ge 0.
\end{cases}
\end{align}

\begin{align}
\mu_{3}(x) & =
\begin{cases}
0.48 + 1.27x + 0.5 \times 7.18x^{2}+ \\
+ 0.7 \times 20.21x^3 + 1.1 \times 21.54x^4 + 1.5 \times 7.33x^5, \;\;\;\;\;\;\;\;\;\;\;\; & \text{if} \;\; x < 0, \\
0.52 + 0.84x - 0.1 \times 3.00x^{2}+ \\
+ 0.3 \times 7.99x^3 - 0.1 \times 9.01x^4 + 3.56x^5, & \text{if} \;\; x \ge 0.
\end{cases}
\end{align}

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by  and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach. For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications. All results presented are based on a 0.95 desired confidence level. Table1 presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$). Table 2 presents similar results for $p=2$ and $q=3$.

\begin{table}[t] \label{Tb1}
\centering
\begin{tabular}{rrrrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
  1   & bootstrap & --0.013 & 0.067 & 0.068 & 0.938       & 0.243     \\
      & CCT       & --0.016 & 0.068 & 0.070 & 0.908       & 0.244     \\
  2   & bootstrap & --0.014 & 0.083 & 0.084 & 0.954       & 0.319     \\
      & CCT       & --0.014 & 0.092 & 0.093 & 0.928       & 0.350     \\
  3   & bootstrap & --0.006 & 0.069 & 0.070 & 0.956       & 0.247     \\
      & CCT       & --0.004 & 0.071 & 0.071 & 0.918       & 0.249     \\
  \bottomrule
\end{tabular}
\caption{Summary of estimates ($p = 1, q = 2$)}
\end{table}

As can be seen on the tables above, the bootstrap bias-correction procedure
proposed in this paper provides a simple alternative to obtain valid robust
confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT.

\begin{table}[t]\label{Tb2}
\centering
\begin{tabular}{rrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
  1   & bootstrap & --0.002 & 0.075 & 0.075 & 0.958       & 0.295     \\
      & CCT       & --0.004 & 0.082 & 0.082 & 0.926       & 0.295     \\
  2   & bootstrap & 0.002   & 0.087 & 0.086 & 0.934       & 0.302     \\
      & CCT       & --0.005 & 0.078 & 0.078 & 0.960       & 0.323     \\
  3   & bootstrap & --0.008 & 0.083 & 0.083 & 0.942       & 0.292     \\
      & CCT       & --0.003 & 0.080 & 0.080 & 0.938       & 0.295     \\
  \bottomrule
\end{tabular}
\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
\end{table}
